POMDP comparisons across sigma_m, sigma_g

### 2018-01-23 appendix/appendix_harvestfirst.Rmd
overestimate

## Simulating the POMDP policies under uncertiainty

@@

>>>>

## Simulating the POMDP policies under uncertainty

@@

-----

## POMDP simulations overestimating measurement uncertainty

pomdp_overest_sims <- 
  map2_dfr(models, alphas, function(.x, .y){
    pomdp_overestimates(transition = .x$transition, 
            model_observation = .x$observation, 
            reward = .x$reward, 
            discount = discount, 
            true_observation <- models[[true]]$observation,
            x0 = x0,
            Tmax = Tmax,
            alpha = .y,
            reps = reps)$df %>% 
              mutate(method = "pomdp") # include a column labeling method
           },
           .id = "scenario"
  )
```
